\Large \bf \sys: Library-Oriented Program Analysis

### 2020-05-22 paper/draft.tex
Update abstract

Dynamic program analysis is a long-standing technique for getting insights into the execution of a program.
This paper presents a new form of dynamic analysis, termed \emph{dialysis}, enabled by the fact that modern dynamic languages feature an import mechanism that loads code at runtime as a string.
Dialysis works by coupling light static transformations with more substantial dynamic ones, inserting hooks for capturing a library's full observable behavior.
% transform and bind their context prior to their evaluation.
% expose instrumentation opportunities to developers.
% This mechanism enables a new lightweight instrumentation technique.
Dialysis offers a new point in the dynamic-analysis trade-off space:
  as it operates at a coarse granularity and does not modify the language runtime environment, it offers better performance and compatibility but foregoes expression-level visibility.
To evaluate its potential, we implement dialysis in LYA and apply it on targets drawn from the JavaScript ecosystem.
Our results show $9.6\times$ performance improvements over state-of-the-art dynamic analysis, compatibility with over 50 libraries and applications, and analyses expressed in under 100LoC---all while offering useful insights on three realistic use-case analyses.

>>>>

Dynamic program analysis is a long-standing technique for obtaining information about program execution.
We present a set of new dynamic analysis techniques that target modern dynamic languages such as Python, Lua, and JavaScript, enabled by the fact that modern dynamic languages feature a module-import mechanism that loads code at runtime as a string.
These techniques use lightweight load-time code transformations that operate on the string representation of the module,
as well as the context to which it is about to be bound, to insert developer-provided, analysis-specific code into the module before it is loaded.
This code implements the dynamic analysis, enabling these techniques to capture all interactions around the library in unmodified production language runtime environments.
We implement these techniques in \sys, a system targeting the JavaScript ecosystem. 
Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.

% operate at the library  interface level  
% This approach occupies an new point in the design trade-off space, enabling lya to operates at the library interface level in unmodified production..

% transform and bind their context prior to their evaluation.
% expose instrumentation opportunities to developers.
% This mechanism enables a new lightweight instrumentation technique.
